Derivative fundamentals

### 2016-06-29 LinearRegression/Documentation/Derivative/Derivative.tex
adding more detail in the tangent vs secant part

    Regrettably this slope does not describe the change of the point very well
    because the line does not touch the function in just one point (this is
    what is a tangent line), insted touch the function two times (this is call a 
    secant line), so this is not what we want. Now the ilustration \\

    \begin{tikzpicture}
        \begin{axis}[
                      xlabel=$x-axis$,
                      ylabel=$y-axis$,
                      xmin=0, xmax=6,
                      ymin=-100, ymax=800,
                      xtick=\empty,
                    ]

>>>>

    Regrettably this slope does not describe the change of the point very well
    because the line does not touch the function in just one point (this is
    what a tangent line is), insted touch the function two times (this is call a
    secant line), this means that the change of the point that we are
    calculating is taking into account two points of the function, not only the
    original point, so this is not what we want. Now the ilustration \\

    \begin{tikzpicture}
        \begin{axis}[
                      xlabel=$x-axis$,
                      ylabel=$y-axis$,
                      xmin=0, xmax=6,
                      ymin=-100, ymax=800,
                      xtick=\empty,
                      ytick=\empty,
                    ]
